### 2016-08-25 ms/ms.tex
added last paragraph to discussion

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not possible. Interestingly, most of the assembling hedgerows did
not undergo a significant reorganization of interactions immediately
the hedgerow was planted (i.e., the transition from weedy field margin
to hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollinator communities (Kremen and
M'Gonigle, in prep).

@@

>>>>

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations. These network organizations
are unlikely to be a product of environmental forces alone because the
network changing points in non-assembling communities are less
frequent, and there are few consistent trends in when change points
occurred across all sites. Several sites had changing points between
year 2009 and 2011 (Fig.~\ref{fig:changePoints}). In California, 2011
marked the beginning of a multi-year drought. In the assembling
hedgerows were not sampled in 2010, so disentangling whether the
changing points are due to skipping a year of assembly or the drought
is not possible. Interestingly, most of the assembling hedgerows did
not undergo a significant interaction reorganization immediately the
hedgerow was planted (i.e., the transition from weedy field margin to
hedgerow). This result is consistent with the finding that in our
study system, hedgerow restoration takes several years to have a
significant impact on the plant-pollinator communities (Kremen and
M'Gonigle, in prep).

@@

Interestingly, though assembling hedgerows had more network
reorganizations than non-assembling communities, pollinator species
and interaction turnover occurred at similar rates across site
types. Only when interactions were weighted by their uniqueness did
assembling hedgerows have higher turnover than non-assembling field
margins. This is likely because though species and interactions are
turning over at the field margins, but pollinator species and
interactions that fill similar roles in the network are replacing each
other. In contrast, at the assembling hedgerows, unique interactions
are turning over as the networks continually
reorganize. Non-assembling mature hedgerow communities, however, had
similar rates of weighted interaction turnover as assembling hedgerows
but also the lowest species turnover. Pollinator communities at mature
hedgerows may be generally more stable, but rare and/or specialized
pollinators could generate this pattern if they entered a community,
formed interactions with plants that did not previously share
pollinators, but did not have high persistence. ANYTHING ELSE? mature
hedgerows are important for conservation or rare species? Maybe?
